# Time Series Forecasting Experiment

## AirPassengers dataset

We will take a look at an Arima model trained on the classic Box & Jenkins airline data. Monthly totals of international airline passengers, 1949 to 1960.

[R-manual](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/AirPassengers.html)

```{r echo=FALSE}
library(datasets)
```

### Load

Let's load the `AirPassengers` dataset
```{r load data}
AirPassengers
```
Indeed, it contains 12 years of passenger arrival totals.

### Split

Let's split it into 10 years for training and 2 for testing.
```{r split}
train = ts(AirPassengers[1:120], start = c(1949, 1), frequency = 12)
test = ts(AirPassengers[121:(121+24-1)], start = c(1959, 1), frequency = 12)
```

### Train

Now we fit an Arima model.
```{r fit}
(fit <- arima(log10(train), c(0, 1, 1),
              seasonal = list(order = c(0, 1, 1), period = 12)))
# update(fit, method = "CSS")
# update(fit, x = window(log10(train), start = 1954))
```

### Predict

Predict and calculate confidence interval
```{r predict}
pred <- predict(fit, n.ahead = 24)
tl <- pred$pred - 1.96 * pred$se
tu <- pred$pred + 1.96 * pred$se
```

### Plot

Plot to look at actual vs prediction vs it's confidence interval.
```{r plot}
ts.plot(train, test, 10^pred$pred, 10^tl, 10^tu, log = "y", lty = c(1, 1, 2, 3, 3))
```

```{r}
## Structural Time Series
# ap <- log10(AirPassengers) - 2
# (fit <- StructTS(ap, type = "BSM"))
# par(mfrow = c(1, 2))
# plot(cbind(ap, fitted(fit)), plot.type = "single")
# plot(cbind(ap, tsSmooth(fit)), plot.type = "single")
```

